---
title: "Homework 5: Iteration"
author: "Kristina Howell"
output: github_document
---

```{r settings, message = FALSE}
# These settings will be used throughout the document.

library(tidyverse)
library(rvest)
library(httr)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis", 
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Problem 1

#### Import the dataset

```{r message=FALSE, warning=FALSE}
homicide_df = 
  read_csv("homicide-data.txt") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

#### Data description

This dataset was collected by the Washington post with a wide range of demographic information about each homicide, the victim, and the outcome of the investigation. It was obtained from the purposes of this report from a publicly available github repository. 

#### Summary Statistics 

```{r message=FALSE, warning=FALSE}
aggregate_df = 
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(), 
    hom_unsolved = sum(resolved == "unsolved")
  )
```

#### Prop testing

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

#### Iteration

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    
    prop_tests = map2(.x = hom_unsolved, 
                      .y = hom_total, 
                      ~prop.test(x = .x, n = .y)), 
    
    tidy_tests = map(.x = prop_tests, 
                     ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

#### Subsequent Data Exploration

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
           geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))
```


## Problem 2

```{r}
list.files("./data")
```




